---
title: "Textual Analysis of Federal Reserve Communications and Crypto Market Volatility: An Augmented GARCH Approach"
format: 
  html: 
    code-fold: true
    code-summary: "show code"
editor: visual
message: false
warning: false
---

### Abstract

The social media has an increasing impact on the financial market. This report use the data from 2024 to 2025, analyses Elon musk's short-term impact of tweets on BTC prices by event study. We find that the

Key words: crypto_currency; Event Study; Behavioral Finance; Social Media

### Introduction

Efficient market financial hypothesis thinks the market price could reflect all available information in the market, but in crypto-currency market, we find that some Key Opinion Leaders' arbitrary comments may influence the price. Among them, Elon Musk is the most powerful KOL. His words can unleash a storm in the market. Is Musk's impact value-motivated or noise trading? Contrary to the prior investigation on the rise and fall, we focus on the variability risk.

### Data & Descriptive statistics

The bit coin data was collected through Binance. And I manually curated the list of tweets.

```{r}
# date acquisition
btc_2024 <- get_binance_full_history("BTCUSDT", start_date = "2024-01-01")

# check the date 
print(head(btc_2024))
print(tail(btc_2024))

# simple plot
plot(btc_2024$Date, btc_2024$Close, type="l", 
     main="BTC Hourly Price (2024 - Present)", 
     xlab="Date", ylab="Price (USDT)")



library(DT)
datatable(btc_2024,
          rownames = FALSE,
          options = list(
            pageLength = 10,
            lengthMenu = c(5,10,20,50),
            searching = TRUE,
            dom = 'Bfrtip',
            buttons = c('copy','csv','excel','pdf','print')
          ))
```

```{r}
library(stargazer)
library(dplyr)
BTC_RET <- btc_2024 |>
  arrange(Date)|>
  mutate(ret = Close /lag(Close)-1)|>
  filter(!is.na(ret))

stargazer(BTC_RET$ret,
          type = "html",
          title = "BTC daily return(specific parameters)",
          digits = 4,
          summary.stat = c("mean","sd","min","max","p25","p75","median"))
```

### Methodology

### 

### Empirical Results

### Discussion& limitations

### Conclusion

### References

### 
