---
title: "Idiosyncratic Volatility and Social Media Sentiment: An Event Study of High-Profile Endorcements in Cryptocurrency Markets"
format: 
  html: 
    code-fold: true
    code-summary: "show code"
editor: visual
message: false
warning: false
---

### Abstract

The social media has an increasing impact on the financial market. This report use the data from 2024 to 2025, analyses Elon musk's short-term impact of tweets on BTC prices by event study. We find that the

Key words: Cryptocurrency; Event Study; Behavioral Finance; Social Media

```{r}
library(quantmod)
library(tidyverse)
library(lubridate)
library(knitr)
library(DT)

# extract the BTC data(sourced from Yahoo Finance)
getSymbols("BTC-USD",src = "yahoo", from = "2024-01-01")

btc_data <- as.data.frame(`BTC-USD`) |>
  rownames_to_column(var = 'Date')|>
  mutate(Date = as.Date(Date))|>
  select(Date, Close_price = `BTC-USD.Close`)

datatable(
  btc_data,
  filter = "top",
  extensions = "Buttons",
  options = list(
    pageLength = 10,
    autoWidth = TRUE,
    dom = "Bfrtip",
    buttons = c("copy","csv","excel","pdf","print")
  )
)
```

### Introduction

Efficient market financial hypothesis thinks the market price could reflect all available information in the market, but in crypto-currency market, we find that some Key Opinion Leaders' arbitrary comments may influence the price. Among them, Elon Musk is the most powerful KOL. His words can unleash a storm in the market. Is Musk's impact value-motivated or noise trading? Contrary to the prior investigation on the rise and fall, we focus on the variability risk.

### Data & Descriptive statistics

The bit coin data was collected by the `quantmod` package from Yahoo Finance. And I manually curated the list of tweets.

```{r}
library(ggplot2)
f1 <-  ggplot(data = btc_data, aes(x = Date, y = Close_price)) +
  geom_line()+
  labs(title = "BTC Daily Closing Price",
       x = "date",
       y = "Closing Price")+
  theme_minimal()

f1

```

```{r}
library(stargazer)
library(dplyr)
BTC_RET <- btc_data |>
  arrange(Date)|>
  mutate(ret = Close_price /lag(Close_price)-1)|>
  filter(!is.na(ret))

stargazer(BTC_RET$ret,
          type = "latex",
          title = "BTC daily return(specific parameters)",
          digits = 4,
          summary.stat = c("mean","sd","min","max","p25","p75","median"))
```

### Methodology

### 

### Empirical Results

### Discussion& limitations

### Conclusion

### References

### 
